Demonstration of matching route networks

### 2024-04-23 r/README.qmd

Basic test

>>>>

# Basic test

```{r}
x = sf::st_sf(
  geometry = sf::st_sfc(
    sf::st_linestring(matrix(c(1, 1, 5, 1), ncol = 2, byrow = TRUE))
  )
)

y = sf::st_sf(
  geometry = c(
    sf::st_sfc(
      sf::st_linestring(matrix(c(2, 2, 6, 2), ncol = 2, byrow = TRUE))
    ),
    sf::st_sfc(
      sf::st_linestring(matrix(c(1, 0.5, 5, 0.5), ncol = 2, byrow = TRUE))
    )
  )
)
x$object = "x"
y$object = "y"
xy = rbind(
  x,
  y
)
plot(xy)
plot(x, add = TRUE)
plot(y)
```

```{r}
matched_df = rnet_match(x, y, dist_tolerance = 1, angle_tolerance = 0, trees = "xy")
matched_df
```

# Another test
